%-------------------------
% Resume in Latex
% Author : Milan Patel
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Milan Patel} & Email : \href{mailto:patelmilan.p@gmail.com}{patelmilan.p@gmail.com}\\
   & Mobile : \href{tel:+917875075461}{+91-7875075461} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Pune}{Pune, India}
      {Bachelor of Science in Computer Science; Grade: First Class}{June. 2005 -- June. 2008}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {K2V2 Technologies}{Pune, India}
      {Software Architect}{Feb 2020 - Nov 2023}
      \resumeItemListStart
        \resumeItem{IRIS - Integrated Real Estate Inventory Management System} \newline
          {Developed and deployed a cutting-edge automated inventory management system for the Real Estate sector, encompassing an Online Booking Engine, comprehensive E-Commerce and Transaction Management, integrated Online and Offline payment solutions, Launch Campaign management, Customer Portal, Bank and Loan management, Negotiations and Offers management, and streamlined Customer Tickets and Requests management.}
        \resumeItem{BeyondWalls - Broker Aggregation Platform} \newline
          {Designed and developed an online platform facilitating collaboration between brokers and real estate builders to enhance sales network expansion. Implemented intelligent incentive plans to maximize sales efficiency and streamlined the entire home buying experience for end users.}
      \resumeItemListEnd

    \resumeSubheading
      {Amura Marketing Technologies}{Pune, India}
      {Product Team Lead}{Sep 2015 - Feb 2020}
      \resumeItemListStart
        \resumeItem{Sell.do - CRM} \newline
          {Architected and launched a fully customizable workflows engine for the company's flagship CRM application tailored for the Real Estate sector, marking the company's inaugural success in automating and overseeing workflows within digital marketing campaigns for real estate enterprises. This innovation has been widely adopted by leading real estate companies in India.}
        \resumeItem{Hawkeye - AdTech Platform} \newline
          {Developed a platform aimed at automating the digital advertising segment within the real estate domain. In conjunction with the Sell.do CRM, the platform offers a comprehensive digital marketing solution for enterprises. It seamlessly integrates with leading Ad platforms such as Google AdWords, Facebook Adverts, and LinkedIn Ads, delivering robust campaign management capabilities and integrated reports for enhanced insights into digital advertising budget utilization.}
      \resumeItemListEnd

% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Magna Infotech Pvt. Ltd. | Retainer for Avaya}{Pune, India}
      {Software Engineer}{Mar 2014 - Sep 2015}
      \resumeItemListStart
        \resumeItem{Avaya Communicator for Microsoft Lync \& MAC OS} \newline
          {Designed, developed, and implemented automation frameworks for Windows and Mac platforms using Python, Ruby, C\#, Microsoft automation libraries, Atomac library, and tools such as Sikuli and Wireshark.}
        \resumeItem{QA Automation}
          {Automated test case execution using Python/Ruby, managed regression and sanity test suites, and generated comprehensive automated test reports crucial for the product release management cycle.}
      \resumeItemListEnd

    \resumeSubheading
      {Bhumi Chemical Industries Pvt. Ltd.}{Nasik, MH, India}
      {Software Engineer}{Jan 2013 - Feb 2014}
      \resumeItemListStart
        \resumeItem{Business Management System}
          {Created a comprehensive web portal tailored for an Offset Printing Ink manufacturing company located in Nasik MIDC, facilitating efficient management of inventory and accounts-related operations.}
      \resumeItemListEnd

    \resumeSubheading
      {ClearGears Inc.}{NYC}
      {Software Developer (Remote)}{Aug 2012 - Dec 2012}
      \resumeItemListStart
        \resumeItem{InterviewJet}
          {Designed and developed a recruitment platform for a Tech Startup, dedicated to connecting talented individuals with opportunities in the vibrant tech industry of New York City.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Academic Project}
  \resumeSubHeadingListStart
    \resumeSubItem{Public Health Records}
      {Platform to manage Electronic Medical Records for Healthcare Professionals}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}
      {Ruby, Python, Javascript, SQL, NoSQL}
    \resumeSubItem{Technologies}
      {RoR, Nodejs, MongoDB, AWS (EC2 \& S3), DO, Ubuntu Server, Passenger + Nginx}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
